\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
fixed bibtex and building issue
Remove duplication where it matters less
Remove word that doesn't make sense

In order to build in the capacity for such responses, the Joystream protocol is built as follows. Shared platform state lives on an open blockchain consensus system. As a result, it has a fully public state and history, and which is fully auditable and immutable. The protocol also has secure direct and broadcast communication capabilities integrated with a platform identity system. This means that it is very cheap for any participant to securely inspect the system, and make irrefutable positive claims as basis part of subsequent public deliberation, learning, debate or agitation. The identity system, along with an immutable history of public actions and communications, generates the incentive to invest in community standing and act with a long time horizon. Further, there is a governance mechanism which allows low cost coordination around how shared assets should be used and regulated, and how the protocol itself should be amended. Importantly this mechanism is self-executing, and thus provides reliable and counterparty free implementation of governance decisions. All of these properties work in concert to support \textit{voice} as response.

@@

\bibliographystyle{unsrt}
\bibliography{assets/singlebibfile}

>>>>

In order to build in the capacity for such responses, the Joystream protocol is built as follows. Shared platform state lives on an open blockchain consensus system. As a result, it has a public state and history, and which is fully auditable and immutable. The protocol also has secure direct and broadcast communication capabilities integrated with a platform identity system. This means that it is very cheap for any participant to securely inspect the system, and make irrefutable positive claims as part of subsequent public deliberation, learning, debate or agitation. The identity system, along with an immutable history of public actions and communications, generates the incentive to invest in community standing and act with a long time horizon. Further, there is a governance mechanism which allows low cost coordination around how shared assets should be used and regulated, and how the protocol itself should be amended. Importantly this mechanism is self-executing, and thus provides reliable and counterparty free implementation of governance decisions. All of these properties work in concert to support \textit{voice} as response.

@@

\bibliographystyle{unsrt}
\bibliography{./assets/singlebibfile}
